On the presentation of orthogonal groups over polynomial rings

### 2019-05-18 dl-paper.tex
Writing proof of the injectivity theorem

\subsection{The proof of the injectivity theorem}
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by
 $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.

\[ \xymatrix{ \overline{\St}(\Phi, A, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \]

\begin{lemma} if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$. \end{lemma}
\begin{proof}
 Lol
\end{proof}

Let $P(\alpha, m)$ be a collection of subsets of $\overline{G}^{\geq 0}_M$ with the following properties:
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha,\ \ g \in P(\alpha, m)\text{ for some $m \in M$}.\]

$P(\alpha, a) P(\alpha, b) \subseteq P(\alpha, a + b)$.
In particular, $P(\alpha, 0)$ is a subgroup.
This hints us that there is a well-defined map $map_\alpha \colon G_M^{\geq 0} \to M$

Let us show that this suffices to verify Steinberg additivity relation:

Consider the set $V' = \St(\Phi, R[X, X^{-1}]) \times \St(\Phi, R[X^{-1}]) \times (1 + M)^*$.
Denote by $V'_0$ the subset of $V'$ consisting of those $(g, h, u)$ for which $\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$.
The the following operator is defined for those $(g, h, u)$, for which $\pi(g, h, u) \in P(\alpha, m)$
\[ T_\alpha(aX^{-1})(g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
                                         h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right),\ 
                                         u(1 + am)\right).\]
We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
 (this operation is well defined for $V'_0$).

@@

If $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $\pi(g, h, u) \in P(\alpha, m) \cap P(\beta, m')$ then
$S_\alpha(a, \pi(g, h, u))\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am})$
%($\beta = 2r$, $\alpha = 1r$, $\gamma = 12$, $\gamma = \alpha - \beta$)
\begin{multline}
 T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
 \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-m'a),\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
 \begin{multline}
 h' = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\frac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am} + \frac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)^{1 -\langle \beta, \alpha \rangle}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
The latter expression is symmetric.

If $\alpha + \beta \in \Phi$, $\pi(g, h, u) \in P(\beta, m) \cap P(\alpha + \beta, m')$ then
\[x_\alpha(-a) \cdot S_\beta(-b, \pi(g, h, u)) h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')) \in P\left(\beta, \frac{m + am'}{1-bm}\right)\]

@@

There is still a mistake in the last implication :(
Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.
\begin{multline}
[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
 T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\frac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
 \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
 = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
 \begin{multline} h' = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\
 \sim  h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
 = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\frac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
 h\cdot x_{\alpha + \beta}\left(\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
\end{multline}

@@

Let us show that F3 and F4 hold automatically.
Suppose $\alpha \perp \beta$, $g \in P(\alpha, m) \cap P(\beta, m')$, then $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$, where 
$g_0 \in P(\alpha, 0) \cap P(\beta, 0)$ (here we use the fact that $P(\alpha, 0)$ (resp. $P(\beta, 0)$) is a subgroup containing $x_{-\beta}(mX)$ (resp. $x_{-\alpha}(m'X)$)).
Then 
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha
  = S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \cdot x_{-\beta}(m'X).\]
We need to show $S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \in P(\beta, 0)$ but this is obvious since the latter is a subgroup.

\printbibliography
\end{document}

>>>>

\subsection{The proof of the injectivity theorem}
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, A[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.

\[ \xymatrix{ \overline{\St}(\Phi, A, M) \ar[r]^{j_+i_+} \ar[d]^{i^-} & \overline{G}_M^{\geq 0} \ar@{^{(}->}[d] \\
              G^{\leq 0} \ar[r]^{j_-} & \St(\Phi, A[X, X^{-1}]), } \] 
Denote by $\overline{G}_M^0$ the image of the left arrow $i_-$ in $G^{\leq 0}$ and by $C$ the set of left cosets of $\overline{G}_M^0$ in $G^{\leq 0}$, i.\,e.
$C = \{ g\overline{G}^0_M \mid g \in G^{\leq 0} \}.$

Denote by $V$ the subset of $\St(\Phi, A[X, X^{-1}]) \times C \times (1 + M)^*$ consisting of those triples $(g, h \overline{G}^0_M, u)$ for which $\pi(g, h, u) = g \cdot j_-(h) \cdot \{ X, u \} \in \overline{G}_M^{\geq 0}$. The correctness of this definition is clear from the above commutative diagram.

The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a  function $T_\alpha(aX^{-1}) \colon V \to V$. This function is defined for those triples $(g, h, u)$ for which $\pi(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$. If $\pi(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $T_\alpha(aX^{-1})$ is defined via the following identity:
\[ T_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\
                                         h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ 
                                         u \cdot (1 + am)\right).\]
It is easy to verify that $\pi(T_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, \pi(g, h, u)).$

The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
 (this operation is well defined for $V'_0$).

@@

If $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $\pi(g, h, u) \in P(\alpha, m) \cap P(\beta, m')$ then
$S_\alpha(a, \pi(g, h, u))\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am})$
%($\beta = 2r$, $\alpha = 1r$, $\gamma = 12$, $\gamma = \alpha - \beta$)
\begin{multline}
 T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
 \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-m'a),\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
 \begin{multline}
 h' = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\frac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am} + \frac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)^{1 -\langle \beta, \alpha \rangle}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
The latter expression is symmetric.
\begin{comment}
If $\alpha + \beta \in \Phi$, $\pi(g, h, u) \in P(\beta, m) \cap P(\alpha + \beta, m')$ then
\[x_\alpha(-a) \cdot S_\beta(-b, \pi(g, h, u)) h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')) \in P\left(\beta, \frac{m + am'}{1-bm}\right)\]

@@

There is still a mistake in the last implication :(
Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.

\begin{multline}
[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
 T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\frac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
 \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
 = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
 \begin{multline} h' = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\
 \sim  h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
 = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\frac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
 h\cdot x_{\alpha + \beta}\left(\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
\end{multline}

@@

Let us show that F3 and F4 hold automatically.
Suppose $\alpha \perp \beta$, $g \in P(\alpha, m) \cap P(\beta, m')$, then $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$, where 
$g_0 \in P(\alpha, 0) \cap P(\beta, 0)$ (here we use the fact that $P(\alpha, 0)$ (resp. $P(\beta, 0)$) is a subgroup containing $x_{-\beta}(mX)$ (resp. $x_{-\alpha}(m'X)$)).
Then 
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha
  = S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \cdot x_{-\beta}(m'X).\]
We need to show $S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \in P(\beta, 0)$ but this is obvious since the latter is a subgroup.
\end{comment}
\printbibliography
\end{document}
